### 2020-05-04 paper/theorems/jordan-lemma/jordan-lemma-path-figure.tex
Restructure text, Switch code language to Julia

\usetikzlibrary{arrows}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{patterns}
%
%
\begin{tikzpicture}
    \begin{axis} [
        axis on top,
        axis lines=middle,
        xmin=-5,
        xmax=5,
        ymin=-5,
        ymax=5,
        unit vector ratio=1 1 1
        ]
%
%        \fill[pattern=north west lines, opacity=0.6] (-10,10) rectangle (2,-10);
%        \fill[white] (2, -3) -- (2, 3) arc(90:270:3) -- cycle;
%        \draw[dashed] (2, -10) -- (2, -3) arc(270:90:3) -- (2,10);
%
%
        \begin{scope}[decoration={
            markings,
            mark=between positions 0 and 1 step 5mm with {\arrow {stealth}}}
            ]
%
            \draw [postaction=decorate] (2,-4) -- (2,4) -- plot [domain=1:3, variable=\t] ({2 + 4*cos(\t * pi / 2 r)}, {4*sin(\t * pi / 2 r)}) -- cycle;
        \end{scope}
        \draw[fill=black] (0, 0) circle (2pt);
    \end{axis}
\end{tikzpicture}
%

>>>>

\usetikzlibrary{arrows}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{patterns}
%
%
\begin{tikzpicture}
    \begin{axis} [
        axis on top,
        axis lines=middle,
        xmin=-5,
        xmax=5,
        ymin=-5,
        ymax=5,
        unit vector ratio=1 1 1
        ]
%
        \fill[pattern=north west lines, opacity=0.6] (-5,5) rectangle (2,-5);
        \fill[white] (2, -1) -- (2, 1) arc(90:270:1) -- cycle;
        \draw[dashed] (2, -5) -- (2, -1) arc(270:90:1) -- (2,5);
%
%
        \begin{scope}[decoration={
            markings,
            mark=between positions 0 and 1 step 5mm with {\arrow {stealth}}}
            ]
%
            \draw [thick, postaction=decorate] plot [domain=1:3, variable=\t] ({2 + 4*cos(\t * pi / 2 r)}, {4*sin(\t * pi / 2 r)});
        \end{scope}
    \end{axis}
\end{tikzpicture}
%
